---
title: "Question 1"
---

We use the Northwind database (file northwind.sqlite) in the question. It provides you with a good database structure and sales data.

See https://www.zentut.com/sql-tutorial/sql-sample-database/ for a diagram.


Database tables
The following explains each table in the Northwind database:

- Customers – stores customer master data
- Orders – stores transaction sale orders from customers
- OrderDetails – stores line items of sale orders
- Products – stores products master data
- Suppliers – stores suppliers master data
- Shippers – stores shippers master data
- Region – stores region master data
- Territories – store territories master data
- Employees – store employees master data
- EmployeeTerritories – store relationship between employee and territory.


Use SQL queries to answer the following questions.



##### (a) Write a query to get Product name and quantity/unit.

```{r}
library(tidyverse)
library(DBI)
library(RSQLite)
library(dplyr)
Nwsql<- dbConnect(RSQLite::SQLite(),dbname='northwind.sqlite')
Nwsql %>% dbListTables()
```


```{sql connection=Nwsql}
SELECT "ProductName", "QuantityPerUnit" FROM "Product"
```



##### (b) Write a query to get discontinued Product list (Product ID and name). 

```{r}
Discontinued <- 
  Nwsql %>%
  tbl("Product")%>%
  filter(Discontinued==1)%>%
  select(ProductName, Id)%>%
  collect()

Discontinued
```

```{sql connection=Nwsql}

SELECT ProductName, Id FROM 'Product'WHERE Discontinued = 1


```



##### (c) Write a query to get Product list (id, name, unit price) where current products cost less than $20.

```{r}
q1c <- 
  Nwsql%>%
  tbl("Product")%>%
  filter(UnitPrice < 20)%>%
  select(ProductName, Id,UnitPrice)%>%
  collect()
q1c 
```

```{sql connection=Nwsql}

SELECT ProductName, Id,UnitPrice FROM 'Product'WHERE UnitPrice < 20

```


##### (d) Write a query to count current and discontinued products.


```{r}
q1d <- 
  Nwsql%>%
  tbl("Product")%>%
  count(Discontinued==1)
 q1d
```
8 prodcuted is discountinued 69 products are not

```{sql connection=Nwsql}

SELECT COUNT(Id) FROM 'Product' WHERE Discontinued=1;
```
```{sql connection=Nwsql}
SELECT COUNT(Id) FROM 'Product' WHERE Discontinued=0;
```


##### (e) Write a query to get most expense and least expensive Product list (name and unit price).

```{r}
q1ea <- 
  Nwsql%>%
  tbl("Product")%>%
  filter(UnitPrice == max(UnitPrice))%>%
  select(ProductName,,UnitPrice)%>%
  collect()

q1ei <- 
  Nwsql%>%
  tbl("Product")%>%
  filter(UnitPrice == min(UnitPrice))%>%
  select(ProductName,,UnitPrice)%>%
  collect()

q1e=full_join(q1ea, q1ei,by = c("ProductName", "UnitPrice"))

q1e
  
```
```{sql connection=Nwsql}


SELECT ProductName,UnitPrice FROM 'Product'ORDER BY UnitPrice DESC LIMIT 1;
```

```{sql connection=Nwsql}
SELECT ProductName,UnitPrice FROM 'Product'ORDER BY UnitPrice ASC LIMIT 1;
```



##### (f) Write a query to get Product list (name, unit price) of above average price


```{r}
q1f <- 
  Nwsql%>%
  tbl("Product")%>%
  filter(UnitPrice >= mean(UnitPrice))%>%
  select(ProductName,,UnitPrice)%>%
  collect()
q1f
```
```{sql connection=Nwsql}

SELECT ProductName,UnitPrice FROM 'Product' 
GROUP BY ProductName
HAVING UnitPrice > ( SELECT AVG (UnitPrice) FROM Product )




```


