---
title: "Question 2"
output:
  html_document:
    df_print: paged
---

Note: You need to be either on the campus or connected to UCD vpn in order to connect the postgres server on alan.ucdavis.edu.

```{r}
library(DBI)
library(dplyr)
chinook <- dbConnect(
  RPostgres::Postgres(),
  dbname = "chinook",
  user = "psqluser", password = "secret", host = "alan.ucdavis.edu"
)
```


The Chinook data model represents a digital media store, including tables for artists, albums, media tracks, invoices and customers.

- Media-related data was created using real data from an Apple iTunes library.
- Customer and employee information was created using fictitious names and addresses that can be located on Google maps, and other well formatted data (phone, fax, email, etc.)
- Sales information was auto generated using random data for a four year period.
- There are 11 tables in the chinook sample database.

  - `Employee` table stores employees data such as employee id, last name, first name, etc. It also has a field named ReportsTo to specify who reports to whom.
  - `Customer` table stores customers data.
  - `Invoice` & `InvoiceLine` tables: these two tables store invoice data. The invoices table stores invoice header data and the invoice line table stores the invoice line items data.
  - `Artist` table stores artists data. It is a simple table that contains only the artist id and name.
  - `Albums` table stores data about a list of tracks. Each album belongs to one artist. However, one artist may have multiple albums.
  - `MediaType` table stores media types such as MPEG audio and AAC audio file.
  - `Genre` table stores music types such as rock, jazz, metal, etc.
  - `Track` table store the data of songs. Each track belongs to one album.
  - `Playlist` & `PlaylistTrack` tables: playlists table store data about playlists. Each playlist contains a list of tracks. Each track may belong to multiple playlists. The relationship between the playlists table and tracks table is many-to-many. The playlist track table is used to reflect this relationship.
  
  See for example https://docs.yugabyte.com/images/sample-data/chinook/chinook-er-diagram.png for a database diagram.


Use both dplyr and SQL code to answer the following questions.


##### (a) What is the title of the album with AlbumId 31?

```{r}

q1=
  chinook%>%
  tbl("Album")%>%
  filter(AlbumId == '31')%>%
  select(Title)%>%
  collect()

chinook%>%
  tbl("Album")

```

```{sql connection=chinook}


SELECT "Title" FROM "Album" WHERE "AlbumId" = 31;

```



##### (b) List all the albums by artists with the word 'black' in their name.


```{r}
library(dplyr)
library(tidyverse)
library(DBI)
library(RSQLite)
library(dplyr)
Album=
  chinook%>%
  tbl("Album")%>%
  collect()

Artist=
  chinook%>%
  tbl("Artist")%>%
  collect()
  
joined=full_join(Album, Artist,by = 'ArtistId')

q1b=
  joined%>%
  filter(grepl("black", str_to_lower(Name)) == TRUE)%>%
  collect()

q1b

```

```{sql connection=chinook}

SELECT a."Title", b."Name" 
  FROM "Album" a
  JOIN "Artist"b
  ON a."ArtistId" = b."ArtistId"
  WHERE "Name" ILIKE '%black%'


```


##### (c) Find the name and length (in seconds) of all tracks that have both length between 30 and 40 seconds, and genre Latin.

```{r}
q2c1=
  chinook%>%
  tbl("Track")

q2c2=
  chinook%>%
  tbl("Genre")

q2c3=full_join(q2c1, q2c2,by = "GenreId")


q2c4= q2c3 %>%select('Name.x','Milliseconds','Name.y')%>%filter(Name.y == 'Latin',Milliseconds>= 30000,Milliseconds <= 40000)

q2c4
```
```{sql connection=chinook}


SELECT a."Name",a."Milliseconds", b."Name" AS "Genre"
  FROM "Track"a
  JOIN "Genre"b
  ON a."GenreId" = b."GenreId"
  WHERE "Milliseconds" >= 30000 AND "Milliseconds" <= 40000 AND b."Name" = 'Latin'

  


```



##### (d) List each country and the number of customers in that country. (You only need to include countries that have customers.)

```{r}
chinook %>% 
  tbl("Customer") %>%
  group_by(Country) %>%
  count(Country)
```
```{sql connection=chinook}

SELECT "Country",COUNT('Country') FROM "Customer" GROUP BY "Country"


```


##### (e) Find the artist (or several artists) with the largest number of countries where the listeners are from. To certain extent, think of the most culturally diverse artists.

```{r}

s1=chinook %>% tbl("InvoiceLine")%>%select(InvoiceId, TrackId)
s2=chinook %>% tbl("Invoice")%>%select(InvoiceId, BillingCountry)
countrys= left_join(s1,s2, by=c('InvoiceId'))

s3=chinook %>% tbl("Track")
track_countrys=left_join(countrys,s3, by=c('TrackId'))

s4=chinook %>% tbl("Album")
countrys_album=left_join(track_countrys,s4, by=c('AlbumId'))

s5=chinook %>% tbl("Artist")
album_artist=left_join(countrys_album,s5, by=c('ArtistId'))


album_artist%>%
  select(Name.y, BillingCountry)%>%
  count(Name.y, BillingCountry)%>%
  group_by(Name.y)%>%
  count()%>%
  arrange(desc(n))

```





```{sql connection=chinook}

SELECT u."BillingCountry",o."Name"
FROM "InvoiceLine"i
Join "Invoice"u
  On i."InvoiceId"=u."InvoiceId"
Join "Track" t
  on i."TrackId" = t."TrackId"
Join "Album" a
  on a."AlbumId" = t."AlbumId"
Join "Artist" o
  on o."ArtistId" = a."ArtistId"
  



  
```




